Flowchart of Current Algorithm

### 2008-10-13 docs/flowchart/paper.tex
updated correct base to account for the fact that we pass in div etarho instead of etarho.  Also stated explicitly for plane-parallel what etarho is

\item {\bf Correct Base}$(\rho_0^{\inp} , \etarho^{\inp}) \rightarrow (\rho_0^{\outp})$
is the process by which we adjust the base state density to account for
large-scale mixing, through $\etarho$

\item[plane-parallel:] We use
\begin{eqnarray}
\rho_{0,j}^{\outp} &=& \rho_{0,j}^{\inp} - \frac{\dt}{\dr} 
\left( \eta_{\rho,j+\myhalf}^{\inp} - \eta_{\rho,j-\myhalf}^{\inp}  \right)  \enskip . 
\end{eqnarray}

@@

\item Define an edge-centered $\etarho^{\nph,\star}$ and cell-centered $\psi_j^{\nph,\star}$:

@@

\begin{eqnarray}
 \etarho^{\nph,\star}   &=&  {\rm {\bf Avg}} \left( (\uadvone \cdotb \er + w_0^{\nph,\star}) 
\rho^{(1),\nph,\star} \right) - w_0^{\nph,\star} \rho_0^{\nph,\star,{\rm pred}} 
 \enskip , \nonumber \\ \\
 \psi_j^{\nph,\star}  &=&  \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^{\nph,\star} + \eta_{\rho,j+\myhalf}^{\nph,\star}\right) g \enskip .
\end{eqnarray}

@@

\item {\bf Correct Base}$(\rho_0^{(2),\star}, \etarho^{\nph,*}) \rightarrow (\rho_0^{n+1,\star})$.

@@

\item Define an edge-centered $ \etarho^{\nph}$ and a cell-centered $\psi_j^{\nph}$,

@@

\begin{eqnarray}
 \etarho^{\nph}   &=&  {\rm {\bf Avg}} \left( (\uadvtwo \cdotb \er + w_0^{\nph}) 
\rho^{(1),\nph} \right) - w_0^{\nph} \rho_0^{\nph,{\rm pred}} \enskip , \\
 \psi_j^{\nph}  &=&  \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^{\nph} + \eta_{\rho,j+\myhalf}^{\nph}\right) g \enskip .
\end{eqnarray}

@@

\item {\bf Correct Base}$(\rho_0^{(2)}, \etarho^{\nph}) \rightarrow (\rho_0^{n+1})$

>>>>

\item {\bf Correct Base}
$[\rho_0^{\inp}, (\nabla\cdot\etarho)^{\inp}] \rightarrow (\rho_0^{\outp})$
is the process by which we adjust the base state density to account for
large-scale mixing, through $\etarho$.  For both plane-parallel and spherical
we use
\begin{equation}
\rho_{0,j}^{\outp} = \rho_{0,j}^{\inp} - \dt (\nabla\cdot\etarho)^{\inp}_j \enskip . 
\end{equation}

@@

\item Define an edge-centered $\etarho^{\nph,\star}$, cell-centered 
$(\nabla\cdot\etarho)^{\nph,\star}$, and cell-centered $\psi_j^{\nph,\star}$:

@@

\begin{eqnarray}
 \etarho^{\nph,\star}   &=&  {\rm {\bf Avg}} \left( (\uadvone \cdotb \er + w_0^{\nph,\star}) 
\rho^{(1),\nph,\star} \right) - w_0^{\nph,\star} \rho_0^{\nph,\star,{\rm pred}} 
 \enskip , \nonumber \\ \\
(\nabla\cdot\etarho)_j^{\nph,\star} &=& 
\frac{\eta_{\rho,j+\myhalf}^{\nph,\star}-\eta_{\rho,j-\myhalf}^{\nph,\star}}{\Delta r} \enskip , \\
 \psi_j^{\nph,\star}  &=&  \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^{\nph,\star} + \eta_{\rho,j+\myhalf}^{\nph,\star}\right) g \enskip .
\end{eqnarray}

@@

\item {\bf Correct Base}
$[\rho_0^{(2),\star}, (\nabla\cdot\etarho)^{\nph,*}] \rightarrow (\rho_0^{n+1,\star})$.

@@

\item Define an edge-centered $\etarho^{\nph}$, cell-centered 
$(\nabla\cdot\etarho)^{\nph}$, and a cell-centered $\psi_j^{\nph}$,

@@

\begin{eqnarray}
 \etarho^{\nph}   &=&  {\rm {\bf Avg}} \left( (\uadvtwo \cdotb \er + w_0^{\nph}) 
\rho^{(1),\nph} \right) - w_0^{\nph} \rho_0^{\nph,{\rm pred}} \enskip , \nonumber \\ \\
(\nabla\cdot\etarho)_j^{\nph} &=& 
\frac{\eta_{\rho,j+\myhalf}^{\nph} - \eta_{\rho,j-\myhalf}^{\nph}}{\Delta r} \enskip , \\
 \psi_j^{\nph}  &=&  \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^{\nph} + \eta_{\rho,j+\myhalf}^{\nph}\right) g \enskip .
\end{eqnarray}

@@

\item {\bf Correct Base}
$[\rho_0^{(2)}, (\nabla\cdot\etarho)^{\nph}] \rightarrow (\rho_0^{n+1})$
